### 2024-04-16 texts/paper_closing.tex
add limitation: no focus on NLPM

\begin{sloppypar}
\printbibliography
\end{sloppypar}
\end{document}

>>>>

\begin{sloppypar}
\printbibliography
\end{sloppypar}

\subsubsection*{Limitations}

For this study, I only investigated the occurence of closure events.
However, private museums can stop existing as private museums not just by closing down, but also by being transformed into other organizational forms.
One way in which this can happen is when other parties, such as local governments other philanthropists, foundations, or corporations become substantially involved in the ownership, governance and/or funding of the museum.
Sometimes this involves changes in the composition of the board of directors, with new parties gaining seats and hence influence in decision-making, thereby diminishing the private character of the museum, often to an extent that it no longer fits the working definition.
Museums which experienced this trajectory have been excluded from the analysis as explorative investigation showed that it was often not feasible to determine the date of such transitions\footnote{As a consequence of this, they are excluded from the analysis alltogether, and thus also not contributing to the the hazard rate for closing, despite being entities at risk for closing. However, as their numbers are limited to 25 entries in the database, the bias this introduces into closing risks is likely not substantial.}
Primarily this was due to the intransparency of these organizations, as well as the gradual process.
As the presence of non-founder members does not categorically exclude a museum from being categorized as private museum as long as third-party influence is limited, this influence can grow until the museum bears little resemblance to its former self.
The possibility of other outcomes than surival and closures has been investigated for NPOs more generally
\parencite{Searing_2020_zombies,HernandezOrtiz_2022_discontinuity,Helmig_Ingerfurth_Pinz_2013_nonprofit}, and for private museums specifically: 
\textcite{Walker_2019_collector} argues that in the case of Germany, private museum founders turn to the state to ensure the survival of their projects in the form of public-private partnerships.
Investigating this process of transformation into a different organizational form thus provides fruitful avenue for further research. 
\end{document}
